% visualization, error

# Error Structure by Visualization

There are often different types of error structures in our data that we don't know about. Visualization can often be a means to detecting them. Here I review a visualization method and how different error structure appears in the visualization.

```{r define_functions}
library(ggplot2)
add_uniform_noise <- function(n_rep, value, sd){
  out_data <- matrix(0, length(value), n_rep)
  for (i_value in seq_along(value)){
    out_data[i_value, ] <- rnorm(n_rep, value[i_value], sd)
  }
  out_data
}

add_prop_noise <- function(n_rep, value, sd){
  out_data <- matrix(0, length(value), n_rep)
  for (i_value in seq_along(value)){
    out_data[i_value, ] <- rnorm(n_rep, value[i_value], value[i_value]*sd)
  }
  out_data
}

add_prop_uniform <- function(n_rep, value, u_sd, p_sd){
    add_uniform_noise(n_rep, value, u_sd) + add_prop_noise(n_rep, value, p_sd)
}

summarize_data <- function(in_data, avg_function = mean){
  mean_val <- apply(in_data, 1, avg_function)
  sd_val <- apply(in_data, 1, sd)
  
  out_data <- data.frame(mean = mean_val, sd = sd_val, rsd = sd_val / mean_val)
}
```


```{r base_data}
# want 100 samples, with 1000 things in each. 
set.seed(1234)
n_point <- 1000
init_values <- runif(n_point, 1, 20)
```


## Error Types

### Uniform

All the same type of error at all values

### Additive

What we normally expect to see, really is a type of **uniform**

```{r additive_data}
n_rep <- 100

add_data <- add_uniform_noise(n_rep, init_values, 0.2)
```

```{r get_stats}
add_summary <- summarize_data(add_data)
ggplot(add_summary, aes(x = mean, y = sd)) + geom_point() + ggtitle("additive SD")

ggplot(add_summary, aes(x = mean, y = rsd)) + geom_point() + ggtitle("additive RSD")

add_data_log <- log(add_data)
add_log_summary <- summarize_data(add_data_log)
ggplot(add_log_summary, aes(x = mean, y = sd)) + geom_point() + ggtitle("log additive SD")
```

### Proportional

Increasing variance with signal, this is not uniform, but is heteroscedastic. Breaks most statistical methods.

```{r proportional_data}
prop_data <- add_prop_noise(n_rep, init_values, 0.01)
prop_summary <- summarize_data(prop_data)
ggplot(prop_summary, aes(x = mean, y = sd)) + geom_point() + ggtitle("proportional SD")
ggplot(prop_summary, aes(x = mean, y = rsd)) + geom_point() + ggtitle("proportional RSD")

prop_log <- log(prop_data)
prop_ls <- summarize_data(prop_log)
ggplot(prop_ls, aes(x = mean, y = sd)) + geom_point() + ggtitle("log proportional SD")
```

### Mixed

```{r mixed_error}
mix_data <- add_prop_uniform(100, init_values, 0.2, 0.1)
mix_summary <- summarize_data(mix_data)
ggplot(mix_summary, aes(x = mean, y = sd)) + geom_point() + ggtitle("mixed SD")
ggplot(mix_summary, aes(x = mean, y = rsd)) + geom_point() + ggtitle("mixed RSD")
```

